Adopting agile in the large: motivations, success factors and challenges

### 2013-11-27 journal/article.tex
Coding process

Based on the research questions and intended focus of the research, we defined
an inclusion criteria with three facets: agile software engineering, focus on
transformation, and large organizations. The first facet covers primary studies
focusing on software engineering organizations applying or striving to apply
agile methods. Examples on topics excluded by the first facet are agile
manufacturing, and applying Scrum practices in management boards. The second
facet states that included studies must provide insights relevant to
organizational transformation, and specifically to the research questions.
The third facet underlines the particular contribution we aim to provide with
this research, namely the exclusive focus on large organizations.

@@

>>>>

Based on the research questions and intended focus of the research, we defined
three facets to guide any inclusion/exclusion decisions: agile software
engineering, focus on transformation, and large organizations. The first facet covers primary studies
focusing on software engineering organizations applying or striving to apply
agile methods. Examples on topics excluded by the first facet are agile
manufacturing, and applying Scrum practices in management boards. The second
facet states that included studies must provide insights relevant to
organizational transformation, and specifically to the research questions.
The third facet underlines the particular contribution we aim to provide with
this research, namely the exclusive focus on large organizations.

@@

\subsection{Coding and synthesis}

An integrated deductive and inductive approach was chosen for coding the primary
studies \cite{Cruzes2011a}. Initially a list of codes was established for the
contextual information, as presented in Table \ref{table:contextualcodes}. The
codes related to the research questions were chosen to be created by an
inductive procedure. The reason for inducting codes rather than using an a
priori approach was to avoid the researchers' previous assumptions of the
research area to affect the choice of codes. To give direction for choosing the
codes seven different code families were established (see Table
\ref{table:codefamilies}), including a description defining the scope of the
families and examples for codes. The example codes would not necessarily be used
as actual codes, and would not represent the entire or final scope of the
families.

\begin{table}[h]
    \begin{tabular}{ p{0.28\textwidth} p{0.7\textwidth} }
        \toprule
        Contextual code     & Explanation   \\
        \midrule

Agile practice & Agile practice or methodology used (eg. Scrum, XP) \\

Business area & The business area in which the organization operates. \\

Organization size & Mentioning the size of the case organization. \\

Time of\newline transformation & When the transformation has been in
progress, or how long the transformation has taken. Possibly relative to
the time of the research. \\

Research process & The paper describes a research process. \\

Geographical\newline location & Where the organization is located. Includes
headquarters and multisite locations. \\

Large scale definition & A definition of "large scale" software development. \\

Measuring results of\newline transformation & Mentioning of how
transormation progress is measured, or how previous indicators have changed. \\

Satisfaction in agile & Internal or external satisfaction/trust/credibility is
mentioned. \\

Multisite / GSD & Mentioning of a multisite organization. This does not imply
that the multisite environment has brought special viewpoints on the agile
implementation. \\

        \bottomrule
    \end{tabular}
    \caption{Context information}
    \label{table:contextualcodes}
\end{table}

\begin{table}[h]
    \begin{tabular}{ p{0.32\textwidth} p{0.65\textwidth} }
        \toprule
        Code family          &  Description
        \\
        \midrule

        RQ1: Reason to change &
        Reasons to start the transformation (demand for shorter
        TTM\footnotemark[1]). \\

		RQ2: Transformation\newline process &
		Statements that describe the transformation process (top-down, big bang,
		stepwise). \\

		RQ3: Challenges &
		Statements that present challenges in the transformation (change resistance).
		\\

		RQ3: Success factors &
		Statements that present success factors in the transformation (management
		support).
		\\

		Investing in change  &
		Factors that present how the organization is investing in the
		transformation (training, consultants, tools). \\

		Practices &
		Distinguishable practices that are used or established during transformation
		(coaching, piloting, continuous integration, communities of practice). Other
		distinguishable factors that are presented as neutral in the primary studies \\

		Other &
		Contextual codes, other codes not relating to RQ's. \\

        \bottomrule
    \end{tabular}
    \caption{Context information}
    \label{table:codefamilies}
\end{table}

\footnotetext[1]{Time To Market}

-- How to choose a code?

-- If the primary source makes an indirect statement relating to a code?

-- Considering that mentioning the inclusion of a factor as a success, then
   would the absence of the same factor be a challenge?

-- If a challenge is described also try to include the resolution in the
   quotation, if one is available. This should broaded the understanding of the
   challenges when looking at the quotations only.

The total accumulated codes and quotes of the integrated deductive and inductive
coding process are presented in Table \ref{table:codecount}.

\begin{table}[h]
    \begin{tabular}{ l r r }
        \toprule
        Code family    &  Codes  &  Quotes
        \\
        \midrule
        RQ1: Reason to change &        10 &   70 \\
		RQ2: Transformation process &  13 &  538 \\
		RQ3: Challenges &              39 &  307 \\
		RQ3: Success factors &         44 &  247 \\
		Investing in change  &          5 &  130 \\
		Practices &                    11 &  160 \\
		Other &                        11 &  194 \\
		Total &                       133 & 1440\footnotemark[2]
		\\
        \bottomrule
    \end{tabular}
    \caption{Context information}
    \label{table:codecount}
\end{table}

\footnotetext[2]{Due to technical reasons a small number of ``free quotations''
is included.}
